---
title: "Iris Analysis"
author: "Mohammad Boaisha"
date: "10/11/2018"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(tidyr)
library(ggplot2)

iris = iris
```
 
# Introduction:
This dataset is derived from [Fisher's](https://en.wikipedia.org/wiki/Iris_flower_data_set) findings. it's a pretty tiny dataset that includes measurements of *Iris* flowers across three species. The purpose of this report is to practice R,```ggplot2``` and rmarkdown basics.


# Dataset structure and notes:
```{r echo=FALSE}
str(iris)
```
As seen, the dataset has an explicit structure of:

Variable             | Data type
---------------------|----------
```Sepal.Length```   | Double
```Sepal.Width```    | Double
```Petal.Length```   | Double
```Petal.Width```    | Double
```Species```        | Factor

The measurements are in **centimeters**




# Visuals:
```{r echo=FALSE}
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point() +
  labs(x = "Sepal's Length",
       y = "Petal's Width",
       title = "Sepal's length vs. Petal's width across three species")
```
